Paper Visualizations

### 2022-05-18 eda/paper-graphics.Rmd
Added table 1

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F, warning = F, message = F, error = F)
library(tidyverse)
library(ggplot2)
library(boxr)
box_auth()

df <- box_read("949901868853", read_fun = readr::read_csv)
```

@@

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F, warning = F, message = F, error = F)
library(tidyverse)
library(ggplot2)
library(boxr)
library(stargazer)
box_auth()

df <- box_read("949901868853", read_fun = readr::read_csv)
amicus <- box_read("947307207905", read_fun = readr::read_csv)
```

@@

# Table 1

```{r, results='asis'}
author_types <- amicus %>% select(chcauf, lifauo, medauf, medauo, legauf, legauo, relauf, relauo) %>%
  mutate(across(where(is.character), as.numeric)) %>%
  summarise(across(where(is.numeric), ~ sum(.x, na.rm = TRUE))) %>%
  pivot_longer(.,cols = c(chcauf, lifauo, medauf, medauo, legauf, legauo, relauf, relauo), names_to = "var", values_to = "ct") %>%
  arrange(var)

author_types <- author_types %>% mutate(author_type = substr(var, 1, 3), position = substr(var, 4, 6)) %>% select(-var)

author_types$position <- ifelse(author_types$position == "auf", 'Reproductive Rights', 'Antiabortion')
author_types <- author_types %>% mutate(`Amicus Author Type` = case_when(
  author_type == 'chc' ~ 'Feminist Organizations',
  author_type == 'lif' ~ 'Anti-Feminist Organizations',
  author_type == 'med' ~ 'Medical Practioners/Orgs/Researchers/Educators',
  author_type == 'leg' ~ 'Legal Organizations',
  author_type == 'rel' ~ 'Religious Groups',
)) %>% select(-author_type)

author_table <- author_types %>% pivot_wider(names_from = position, values_from = ct)
author_table[1,3] <- 0
author_table[3,2] <- 0

stargazer(author_table, summary=FALSE, rownames=FALSE, title = "Table 1.  Total Number of Amicus Briefs by Amicus Type in the Supreme Court Abortion Cases", notes = "a. Legal cases can have more than one amicus type filed in a case (e.g., differing groups of feminist organizations can file more than one brief in a case).  Also, the same organizations file briefs in multiple cases.", header=FALSE, notes.align = 'c')
```
